---
title: "Toddler Uncertainty Monitoring"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of toddler uncertainty monitoring study.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
setwd("~/Desktop/tadpole_t1_data/analysis")
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr)
library(dplyr)
library(RWiener)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(xtable)
library(knitr)
library(markdown)
theme_set(theme_bw())
```

Read in data file.

```{r}
d.raw_et <- read.csv("AllSubs_ET.csv", header = TRUE) 
d.raw_et$ID <- d.raw_et$Subject_ID 

d.raw_sw <- read.csv("perceptual_transitions.csv", header = TRUE)
d.raw_sw$ID <- d.raw_sw$Subject
```

Make data tidy.

```{r}
d.raw_et <- d.raw_et %>%
  gather(trial, acc, acc1:acc20) %>%
  select(-Subject_ID) 

d.raw_et$trial <-str_replace(d.raw_et$trial, "acc","")

d.raw_sw <- d.raw_sw %>%
  gather(trial, trans, Trial1:Trial20) %>%
  select(-Subject) 
  
d.raw_sw$trial <- str_replace(d.raw_sw$trial, "Trial","")

d_et <- d.raw_et %>%
  left_join(d.raw_sw) 

d_et$acc[d_et$acc==999] <- NA
```

Read in trial info, demographics, and word familiarity.

```{r}
demo <- read.csv("demographics.csv") 
trial_info <- read.csv("conditions.csv", header = TRUE)
trial_info$trial <- as.character(trial_info$trial)

word_fam_key <- read.csv("word_fam_key.csv")
word_fam_key$trial <- as.character(word_fam_key$trial)

word_fam <- read.csv("word_familiarity.csv") %>%
  gather("target", "familiarity", 2:41 )

response_key <- read.csv("response_key.csv")
response_key$trial <- as.character(response_key$trial)
```

Join trial info and demographics with raw data.

```{r}
d_et <- left_join(d_et, trial_info) %>%
  left_join(demo) %>%
  select(-participation_date, -birthdate) %>%
  left_join(word_fam_key) %>%
  left_join(word_fam) %>%
  left_join(response_key)

d_et <- d_et %>% 
  mutate(similar = ifelse(similarity == 1, "high-similarity",
                                       "low-similarity")) %>%
  select(-similarity)
```


Descriptives.

Filter fast and slow RTs, missing data, unfamiliar trials.

```{r}
d_et_filt <- d_et %>% 
  filter(!is.na(acc), 
         familiarity != 0)

d_et_filt$acc <- as.character(d_et_filt$acc)
```


Descriptives.

```{r}
d_et_filt$acc <- as.numeric(d_et_filt$acc)

ms <- d_et_filt %>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms, aes(x = factor(similar), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Similarity") + 
  ylab("Proportion Accurate")

d$acc <- as.factor(d$acc)
ms <- d_et_filt %>%
  group_by(acc, similar)%>%
  multi_boot_standard(col = "trans", na.rm = TRUE)

ggplot(ms, aes(x = factor(acc), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Accuracy") + 
  ylab("Number of switches") + 
  facet_wrap(~similar)
```

```{r}
glm_maximal_mod <- lmer(trans ~ acc * similar +
                           (acc * similar | ID), 
                         data = d_et_filt)

coefs <- data.frame(coef(summary(glm_maximal_mod)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs
```

