---
title: "Toddler Uncertainty Monitoring"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of toddler uncertainty monitoring study.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
setwd("~/Desktop/tadpole_t1_data/analysis")
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr)
library(dplyr)
library(RWiener)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(xtable)
library(knitr)
library(markdown)
theme_set(theme_bw())
```

Read in data file.

```{r}
d.raw <- read.table("AllSubs.txt", header = TRUE) %>% 
```

Make data tidy.

```{r}
d_acc<- d.raw %>%
  select(Subject_ID, acc1, acc2, acc3, acc4, acc5, acc6, acc7, acc8, acc9, acc10, acc11, acc12, acc13, acc14, acc15, acc16, acc17, acc18, acc19, acc20)%>%
  gather(trial, acc, acc1:acc20) 

d_rt <- d.raw %>%
  select(Subject_ID, RT1, RT2, RT3, RT4, RT5, RT6, RT7, RT8, RT9, RT10, RT11, RT12, RT13, RT14, RT15, RT16, RT17, RT18, RT19, RT20) %>%
  gather(trial, RT, RT1:RT20) 

d_acc$trial <-str_replace(d_acc$trial, "acc","")
d_rt$trial <- str_replace(d_rt$trial, "RT","")

d <- d_acc %>%
  left_join(d_rt) 

d$acc[d$acc==999] <- NA
```

Read in trial info and demographics. 

```{r}
# demo <- read.csv("demographics.csv") 
trial_info <- read.csv("conditions.csv", header = TRUE)
trial_info$trial <- as.character(trial_info$trial)
```

Join trial info and demographics with raw data.

```{r}
d <- left_join(d, trial_info)

d <- d %>% 
  mutate(similarity_condition = ifelse(similarity == 1, "high-similarity",
                                       "low-similarity"))
```

Descriptives.

```{r}
ms <- d %>%
  filter(!is.na(similarity))%>%
  group_by(similarity)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms, aes(x = factor(similarity), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Difficulty") + 
  ylab("Mean Accuracy")

ms <- d %>%
  filter(!is.na(similarity))%>%
  group_by(similarity)%>%
  multi_boot_standard(col = "RT", na.rm = TRUE)

ggplot(ms, aes(x = factor(similarity), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Difficulty") + 
  ylab("Mean Reaction Time (ms)") 


levels(d$similarity)[0] <- "low"
levels(d$similarity)[1] <- "high"

d$acc <- as.factor(d$acc)
ms <- d %>%
  filter(!is.na(acc))%>%
  group_by(acc, similarity)%>%
  multi_boot_standard(col = "RT", na.rm = TRUE)


levels(ms$similarity)[0] <- "low"
levels(ms$similarity)[1] <- "high"

ggplot(ms, aes(x = factor(acc), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Accuracy") + 
  ylab("Mean Reaction Time (ms)") + 
  facet_wrap(~similarity, labeller = label_both)
```

Filter fast and slow RTs

```{r}
d_filt <- d %>% 
  filter(RT < mean(RT) + 3 * sd(RT), 
         RT > mean(RT) - 3 * sd(RT),
         RT >= 200,
         !is.na(acc))
```

Plot correct and incorrect RT distributions

```{r}
ggplot(aes(x = RT, fill = acc), 
       data = filter(d_filt, !is.na(acc))) +
  geom_density(alpha = 0.7, adjust = 1.5) + 
  facet_grid(.~similarity) 
```

# Drift Diffusion Analysis

Workflow taken from Nordmeyer et al. (2016). The goal is to estimate parameters separately for each participant and then we aggregate across participants to get means & confidence intervals on the parameters.

The parameters of the drift drift diffusion model are: 

* $\alpha$ = boundary separation: speed-accuracy tradeoff (higher values mean higher accuracy)
* $\beta$ = initial bias
* $\delta$ = drift rate: speed of information processing (close to zero means ambiguous information)
* $\tau$ = nondecision time: motor response time

## Estimating parameters

```{r setuppars}
# get the data we care about and format for Rwiener functions
# columns need to be named "q" for RT and "resp" for response
d_ddm <- d_filt %>% 
  filter(RT <= 6000, RT >= 600) %>% 
  mutate(RT_sec = RT / 1000) %>% 
  select(Subject_ID, similarity_condition, RT_sec, acc) %>% 
  dplyr::rename(q = RT_sec)

levels(d_ddm$acc) <- list(lower="0", upper="1")

d_ddm <- d_ddm %>% mutate(resp = acc)
```

```{r}
sub.pars <- data.frame(Separation = numeric(),
                       Non.Decision = numeric(),
                       Bias = numeric(),
                       Drift = numeric(),
                       Similarity = character(),
                       Sub.Num = character(),
                       stringsAsFactors = F)

#because RWiener is finicky:
d_ddm$resp <- as.character(d_ddm$resp)
```

```{r estpars}
conditions <- unique(as.character(d_ddm$similarity_condition))
subs <- unique(as.character(d_ddm$Subject_ID)) 
sub.pars.final <- data.frame()

for (j in 1:length(subs)) {
  sid <- as.character(subs[j]) 
  print(sid)
  dat <- as.data.frame(filter(d_ddm, Subject_ID == sid))
    # fit ddm for each participant
    # and for each condition run
  for (cond in 1:length(conditions)) {
    dat_cond <- filter(dat, similarity_condition == conditions[cond])
    condition_type <- conditions[cond]
    print(condition_type)
    opt <- optim(c(1, .1, .1, 1), wiener_deviance, 
              dat=select(dat_cond, c(q, resp)), method="Nelder-Mead")
    pars <- c(opt$par, condition_type, sid)
    sub.pars[cond,] <- pars
  }
  sub.pars.final <- rbind(sub.pars.final, sub.pars)  
} 
```

### Plot Parameters

This plot shows the mean parameter values & 95% C.I.s for each stimuli type

```{r plotpars, fig.width=8, fig.height=6}
sub.pars.final$Separation <- as.numeric(sub.pars.final$Separation)
sub.pars.final$Non.Decision <- as.numeric(sub.pars.final$Non.Decision)
sub.pars.final$Bias <- as.numeric(sub.pars.final$Bias)
sub.pars.final$Drift <- as.numeric(sub.pars.final$Drift)

sub.pars.final <- sub.pars.final %>% 
  group_by(Similarity) %>%
  filter(Separation < mean(Separation) + 3 * sd(Separation), 
         Separation > mean(Separation) - 3 * sd(Separation)) %>%
  filter(Non.Decision < mean(Non.Decision) + 3 * sd(Non.Decision), 
         Non.Decision > mean(Non.Decision) - 3 * sd(Non.Decision)) %>%
  filter(Bias < mean(Bias) + 3 * sd(Bias), 
         Bias > mean(Bias) - 3 * sd(Bias)) %>%
  filter(Drift < mean(Drift) + 3 * sd(Drift), 
         Drift > mean(Drift) - 3 * sd(Drift)) %>%
  ungroup() %>%
  na.omit()

sub.pars.final <- sub.pars.final %>%  gather(Param, Value, Separation:Drift)
```

Plot distributions of parameters across conditions

```{r}
ggplot(aes(x = Value, fill = Similarity), 
       data = filter(sub.pars.final, Param %in% c("Drift", "Separation"))) +
  geom_density(alpha = 0.7, adjust = 1.5) + 
  facet_grid(.~Param, scales = "free") +
  scale_fill_solarized()
```

Get means and CIs for parameter values and plot

```{r}
sub.pars.ms <- sub.pars.final %>%
  group_by(Similarity, Param) %>%
  multi_boot_standard(column = "Value", empirical_function = "mean")

ggplot(aes(x = Similarity, y = mean), 
       data = filter(sub.pars.ms)) +
  geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~Param, scales = "free") +
  scale_fill_solarized() + 
  ylab("Mean Param Value") +
  guides(fill = F) 
```


