---
title: "Toddler Uncertainty Monitoring"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of toddler uncertainty monitoring study.

# Data preprocessing

Preliminaries.

```{r, include = FALSE}
setwd("~/Desktop/tadpole_t1_data/analysis/26-30-mos/")
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr)
library(dplyr)
library(RWiener)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(xtable)
library(knitr)
library(markdown)
library(psych)
library(Hmisc)
library(magrittr)

theme_set(theme_bw())
```

```{r, include = FALSE}

#sets up function to produce correlation table with significance stars.
corstarsl <- function(x){ 
  require(Hmisc) 
  x <- as.matrix(x) 
  R <- rcorr(x)$r 
  p <- rcorr(x)$P 
  
  ## define notions for significance levels; spacing is important.
  mystars <- ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "* ", " ")))
  
  ## trunctuate the matrix that holds the correlations to two decimal
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1] 
  
  ## build a new matrix that includes the correlations with their apropriate stars 
  Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x)) 
  diag(Rnew) <- paste(diag(R), " ", sep="") 
  rownames(Rnew) <- colnames(x) 
  colnames(Rnew) <- paste(colnames(x), "", sep="") 
  
  ## remove upper triangle
  Rnew <- as.matrix(Rnew)
  Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
  Rnew <- as.data.frame(Rnew) 
  
  ## remove last column and return the matrix (which is now a data frame)
  Rnew <- cbind(Rnew[1:length(Rnew)-1])
  return(Rnew) 
}
```
Read in trial info, demographics, and word familiarity.

```{r}
demo <- read.csv("demographics.csv") 
trial_info <- read.csv("conditions.csv", header = TRUE)
trial_info$trial <- as.character(trial_info$trial)

word_fam_key <- read.csv("word_fam_key.csv")
word_fam_key$trial <- as.character(word_fam_key$trial)

word_fam <- read.csv("word_familiarity.csv") %>%
  gather("target", "familiarity", 2:41 )

response_key <- read.csv("response_key.csv")
response_key$trial <- as.character(response_key$trial)
```

Read in TS data file.

```{r}
d.raw_ts <- read.table("AllSubs_TS.txt", header = TRUE) 
```

Make TS data tidy.

```{r}
d_acc_ts<- d.raw_ts %>%
  select(Subject_ID, acc1, acc2, acc3, acc4, acc5, acc6, acc7, acc8, acc9, acc10, acc11, acc12, acc13, acc14, acc15, acc16, acc17, acc18, acc19, acc20)%>%
  gather(trial, acc, acc1:acc20) 

d_rt <- d.raw_ts %>%
  select(Subject_ID, RT1, RT2, RT3, RT4, RT5, RT6, RT7, RT8, RT9, RT10, RT11, RT12, RT13, RT14, RT15, RT16, RT17, RT18, RT19, RT20) %>%
  gather(trial, RT, RT1:RT20) 

d_acc_ts$trial <-str_replace(d_acc_ts$trial, "acc","")
d_rt$trial <- str_replace(d_rt$trial, "RT","")

d_ts <- d_acc_ts %>%
  left_join(d_rt) %>%
  mutate(ID = Subject_ID) %>%
  select(ID, RT, acc, trial)

d_ts$acc[d_ts$acc==999] <- NA
```

Join trial info and demographics with raw TS data.

```{r}
d_ts <- left_join(d_ts, trial_info) %>%
  left_join(demo) %>%
  select(-participation_date, -birthdate) %>%
  left_join(word_fam_key) %>%
  left_join(word_fam) %>%
  left_join(response_key) %>%
  filter(drop != 1)

d_ts <- d_ts %>% 
  mutate(similar = ifelse(similarity == 1, "similar",
                                       "dissimilar")) %>%
  select(-similarity)
d_ts$ID <- as.factor(as.character(d_ts$ID))
```

There are `r length(levels(d_ts$ID))` touchscreen participants.

Read in ET data. 

```{r}
d.raw_et <- read.csv("AllSubs_ET.csv", header = TRUE) 
d.raw_sw <- read.csv("perceptual_transitions.csv", header = TRUE)
d.raw_sw$ID <- d.raw_sw$Subject
```

Make data ET tidy.

```{r}
d.raw_sw <- d.raw_sw %>%
  gather(trial, trans, Trial1:Trial20) %>%
  select(-Subject) 
d.raw_sw$ID <- as.factor(as.character(d.raw_sw$ID))
d.raw_et$ID <- as.factor(as.character(d.raw_et$ID))
d.raw_sw$trial <- str_replace(d.raw_sw$trial, "Trial","")
d.raw_et$trial <- as.character(d.raw_et$trial)
d.raw_sw$ID <- as.character(d.raw_sw$ID)
d.raw_et$ID <- as.character(d.raw_et$ID)
demo$ID <- as.character(demo$ID)
word_fam$ID <- as.character(word_fam$ID)
```

Join ET transitions and accuracy data and drop excluded participants (including pilots).

```{r}
d.raw_et <- d.raw_et %>%
  select(ID, trial, acc)

d_et <- d.raw_et %>%
  inner_join(d.raw_sw) %>%
  mutate(acc_et = acc) %>%
  left_join(demo) %>%
  left_join(trial_info)%>%
  select(-participation_date, -birthdate) %>%
  left_join(word_fam_key) %>%
  left_join(word_fam) %>%
  left_join(response_key) %>%
  filter(drop != 1) %>%
  select(-acc)

#recode similarity from 1s and 0s to string.
d_et <- d_et %>% 
  mutate(similar = ifelse(similarity == 1, "similar",
                                       "dissimilar")) %>%
  select(-similarity)
d_et$ID <- as.factor(as.character(d_et$ID))
```

There are `r length(levels(d_et$ID))` eyetracker participants.

Merge TS and ET data and drop excluded participants (including pilots).

```{r}
d <- d_ts %>%
  full_join(d_et) %>%
  filter(drop != 1)
d$ID <- as.factor(as.character(d$ID))
```

There are `r length(levels(d$ID))` participants with *either* eyetracker or touchscreen data.

#Demographics

```{r, include = FALSE}
#remove dropped participants
demo_drop <- demo %>%
  filter(drop != 1)

demo_drop$income <- str_replace(demo_drop$income,"f ","f")
#meaningful income labels.
demo_drop$income <- str_replace(demo_drop$income,"a","<15,000")
demo_drop$income <- str_replace(demo_drop$income,"b","15,000-25,000")
demo_drop$income <- str_replace(demo_drop$income,"c","25,000-40,000")
demo_drop$income <- str_replace(demo_drop$income,"d","40,000-60,000")
demo_drop$income <- str_replace(demo_drop$income,"e","60,000-90,000")
demo_drop$income <- str_replace(demo_drop$income,"f",">90,000")

demo_drop$income <- factor(demo_drop$income, levels = c("","<15,000","15,000-25,000","25,000-40,000","40,000-60,000","60,000-90,000",">90,000"))
```

Summaries of income, race, gender, and age in months.
```{r}
summary(demo_drop$income)
summary(demo_drop$race)
summary(demo_drop$gender)
psych::describe(demo_drop$age_months)

```

#Eyetracker task

Filter missing data and unfamiliar trials. 

```{r}
d_et_filt <- d_et %>% 
  mutate(acc = acc_et)%>%
  select(-acc_et)%>%
  filter(!is.na(trans),
         !is.na(acc),
         familiarity != 0)
```

##Descriptives

Transitions for accurate and inaccurate
```{r}
psych::describeBy(d_et_filt$trans, d_et_filt$acc)
```

Transitions for similar and dissimilar
```{r}
psych::describeBy(d_et_filt$trans, d_et_filt$similar)
```

Accuracy for similar and dissimilar
```{r}
psych::describeBy(d_et_filt$acc, d_et_filt$similar)
```

Plot accuracy. 
```{r}
ms <- d_et_filt %>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms, aes(x = factor(similar), y = mean, fill = similar)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Similarity") + 
  ylab("Proportion Accurate") + ggtitle("Eyetracker Accuracy")
```

Plot distribution (density) of switches by accuracy and similarity.
```{r, echo=FALSE}
d_et_filt$acc <- as.factor(d_et_filt$acc)

ggplot(aes(x = trans, fill = acc), 
       data = d_et_filt) +
  geom_density(alpha = 0.7, adjust = 1.5) + 
  facet_grid(.~similar) 
```

Plot the mean number of switches by accuracy and similarity.

```{r, echo=FALSE}
d_et_filt$acc <- as.factor(as.character(d_et_filt$acc))

ms <- d_et_filt %>%
  group_by(acc, similar)%>%
  multi_boot_standard(col = "trans", na.rm = TRUE)

ggplot(ms, aes(x = factor(acc), y = mean, fill = acc)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Accuracy") + 
  ylab("Number of switches") + 
  facet_wrap(~similar)
```

##Analyses

T-tests

Effect of similarity on switches among accurate trials.
```{r, echo= FALSE}
t.test(subset(d_et_filt, acc==1 & similar=="similar")$trans, 
       subset(d_et_filt, acc==1 & similar=="dissimilar")$trans)
```

Effect of similarity on switches among inaccurate trials.
```{r, echo= FALSE}
t.test(subset(d_et_filt, acc==0 & similar=="similar")$trans, 
       subset(d_et_filt, acc==0 & similar=="dissimilar")$trans)
```

Effect of accuracy on switches among similar trials.
```{r, echo= FALSE}
t.test(subset(d_et_filt, acc==1 & similar=="similar")$trans, 
       subset(d_et_filt, acc==0 & similar=="similar")$trans)
```

Effect of accuracy on switches among dissimlar trials.
```{r, echo= FALSE}
t.test(subset(d_et_filt, acc==1 & similar=="dissimilar")$trans, 
       subset(d_et_filt, acc==0 & similar=="dissimilar")$trans)
```

Effect of accuracy on switches overall
```{r, echo= FALSE}
t.test(subset(d_et_filt, acc==1)$trans, 
       subset(d_et_filt, acc==0)$trans)
```

Effect of similarity on switches overall
```{r, echo= FALSE}
t.test(subset(d_et_filt, similar=="dissimilar")$trans, 
       subset(d_et_filt, similar=="similar")$trans)
```

Do individual differences in RT differential (for similar vs. dissimilar) correlate with accuracy? 

```{r}
d_et_filt$acc <- as.numeric(as.character(d_et_filt$acc))

d_et_filt_id <- d_et_filt %>%
  group_by(ID) %>%
  mutate(trans_acc = mean(trans[acc == 1])) %>%
  mutate(trans_inacc = mean(trans[acc == 0])) %>%
  mutate(trans_sim = mean(trans[similar == "similar"])) %>%
  mutate(trans_dissim = mean(trans[similar == "dissimilar"])) %>%
  mutate(trans_acc_diff = trans_inacc - trans_acc) %>%
  mutate(trans_sim_diff = trans_sim - trans_dissim) %>%
  mutate(avg_acc = mean(acc))
```

Correlate differentials with accuracy.

```{r, echo = FALSE}
d_et_filt_id <- d_et_filt_id %>%
  select(ID, trans_acc_diff, trans_sim_diff, avg_acc) %>%
  distinct %>%
  ungroup %>%
  select(-ID)

corstarsl(d_et_filt_id)
```

##Summary of Eyetracker Results

Accuracy was higher for dissimilar items.

T-tests revealed a significant effect of similarity and a marginal effect of accuracy on switches.

Individual differences in transitions differentials (i.e., transitions for similar - similar; trans for inacc - acc) were correlated with each other but not with accuracy. This is expected as accuracy and similarity are correlated. 

#Touchscreen task

Filter fast and slow RTs, missing data, unfamiliar trials.

```{r}
top_bound <- mean(log(d_ts$RT)) + 3*sd(log(d_ts$RT))
bottom_bound <- mean(log(d_ts$RT)) - 3*sd(log(d_ts$RT))

d_filt_rt <- d_ts %>%
  filter(log(RT) < top_bound, 
         log(RT) > bottom_bound,
         !is.na(acc),
         familiarity != 0)

d_filt_rt_log <- d_filt_rt %>%
  mutate(RT = log(RT))
```

##Descriptives

```{r}
psych::describeBy(d_filt_rt_log$RT, d_filt_rt_log$acc)
psych::describeBy(d_filt_rt_log$RT, d_filt_rt_log$similar)
psych::describeBy(d_filt_rt_log$acc, d_filt_rt_log$similar)
```

```{r}
ms <- d_filt_rt %>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms, aes(x = factor(similar), y = mean, fill = similar)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Similarity") + 
  ylab("Proportion Accurate") + ggtitle("Touchscreen Accuracy")
```

Plot RT distribution (density) by accuracy and similarity.

```{r, echo=FALSE}
d_filt_rt$acc <- as.factor(d_filt_rt$acc)

ggplot(aes(x = RT, fill = acc), 
       data = d_filt_rt) +
  geom_density(alpha = 0.7, adjust = 1.5) + 
  facet_grid(.~similar) 
```

Plot mean RT by accuracy and similarity.

```{r, echo=FALSE}
d_filt_rt$acc <- as.factor(as.character(d_filt_rt$acc))

ms <- d_filt_rt %>%
  filter(!is.na(acc))%>%
  group_by(acc, similar)%>%
  multi_boot_standard(col = "RT", na.rm = TRUE)

ggplot(ms, aes(x = factor(acc), y = mean, fill = acc)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Accuracy") + 
  ylab("Mean Reaction Time (ms)") + 
  facet_wrap(~similar)
```

##Analyses

T-tests
```{r, echo= FALSE}
#t.tests

#effect of similarity on RT among accurate trials.
t.test(subset(d_filt_rt_log, acc==1 & similar=="similar")$RT, 
       subset(d_filt_rt_log, acc==1 & similar=="dissimilar")$RT)

#effect of similarity on RT among inaccurate trials.
t.test(subset(d_filt_rt_log, acc==0 & similar=="similar")$RT, 
       subset(d_filt_rt_log, acc==0 & similar=="dissimilar")$RT)

#effect of accuracy on RT among similar trials.
t.test(subset(d_filt_rt_log, acc==1 & similar=="similar")$RT, 
       subset(d_filt_rt_log, acc==0 & similar=="similar")$RT)

#effect of accuracy on RT among dissimlar trials.
t.test(subset(d_filt_rt_log, acc==1 & similar=="dissimilar")$RT, 
       subset(d_filt_rt_log, acc==0 & similar=="dissimilar")$RT)

#effect of accuracy on RT overall
t.test(subset(d_filt_rt_log, acc==1)$RT, 
       subset(d_filt_rt_log, acc==0)$RT)

#effect of similarity on RT overall
t.test(subset(d_filt_rt_log, similar=="dissimilar")$RT, 
       subset(d_filt_rt_log, similar=="similar")$RT)
```

Linear mixed-effects models predicting RT based on similarity and accuracy.

```{r}
#more complex random effects structures fail to converge.
#expect random effects slopes to vary more for ID than target- effects of similarity and accuracy should vary more by participant than target.

# glm_RT_full <- lmer(RT ~ similar + acc +
#                           (similar + acc | ID), 
#                          data = d_filt_rt_log, REML = FALSE)
# 
# glm_RT_interaction <- lmer(RT ~ similar * acc +
#                           (similar + acc | ID), 
#                          data = d_filt_rt_log, REML = FALSE)
# 
# glm_RT_sim <- lmer(RT ~ similar +
#                           (similar + acc | ID), 
#                          data = d_filt_rt_log, REML = FALSE)
# 
# glm_RT_acc <- lmer(RT ~ acc +
#                           (similar + acc | ID), 
#                          data = d_filt_rt_log, REML = FALSE)
# 
# glm_RT_age <- lmer(RT ~ similar + acc + age_months +
#                           (similar + acc | ID), 
#                          data = d_filt_rt_log, REML = FALSE)
# 
# glm_RT_age_sim <- lmer(RT ~  acc + similar * age_months +
#                           (similar + acc | ID), 
#                          data = d_filt_rt_log, REML = FALSE)
# 
# glm_RT_age_acc <- lmer(RT ~ similar + acc * age_months +
#                           (similar + acc | ID), 
#                          data = d_filt_rt_log, REML = FALSE)
```

Summary of maximal model (with interaction term)
```{r}
# summary(glm_RT_interaction)
```

Fixed effects coeffiencients for full model.
```{r, echo = FALSE}
# kable(summary(glm_RT_full)$coefficients, digits = 2)
```

Compare model fits as significance test.

Test for effect of accuracy.
```{r, echo=FALSE}
# kable(anova(glm_RT_full, glm_RT_sim))
# 
# acc_effect <- anova(glm_RT_full, glm_RT_sim)
# acc_effect$p <- as.numeric(acc_effect$`Pr(>Chisq)`[2])
```

Do individual differences in RT differential (for similar vs. dissimilar) correlate with accuracy? 

```{r}
d_filt_rt$acc <- as.numeric(as.character(d_filt_rt$acc))

d_filt_rt_id <- d_filt_rt %>%
  group_by(ID) %>%
  mutate(rt_acc = mean(RT[acc == 1])) %>%
  mutate(rt_inacc = mean(RT[acc == 0])) %>%
  mutate(rt_sim = mean(RT[similar == "similar"])) %>%
  mutate(rt_dissim = mean(RT[similar == "dissimilar"])) %>%
  mutate(rt_acc_diff = rt_inacc - rt_acc) %>%
  mutate(rt_sim_diff = rt_sim - rt_dissim) %>%
  mutate(avg_acc = mean(acc))
```

Correlate differentials with accuracy.

```{r, echo = FALSE}
d_filt_rt_id <- d_filt_rt_id %>%
  select(ID, rt_acc_diff, rt_sim_diff, avg_acc) %>%
  distinct %>%
  ungroup %>%
  select(-ID)

corstarsl(d_filt_rt_id)
```

Individual differences in RT differentials (i.e., RT for similar - similar; RT for inacc - acc) were correlated with each other but not with accuracy. This is expected as accuracy and similarity are correlated. 

##Summary of Touchscreen Results

Accuracy was higher for dissimilar items.

T-tests showed significant effect of accuracy on RT and marginal effect of similarity on RT.

Individual differences in RT differentials (i.e., RT for similar - similar; RT for inacc - acc) were correlated with each other but not with accuracy. This is expected as accuracy and similarity are correlated. 
