---
title: "Toddler Uncertainty Monitoring"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of toddler uncertainty monitoring study.

# Data preprocessing

Preliminaries.

```{r echo=FALSE}
setwd("~/Desktop/tadpole_t1_data/analysis/26-30-mos/")
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(langcog)
library(plyr)
library(dplyr)
library(RWiener)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(xtable)
library(knitr)
library(markdown)
library(psych)
theme_set(theme_bw())
```

Read in RT data file.

```{r}
d.raw_ts <- read.table("AllSubs_TS.txt", header = TRUE) 
```

Make data tidy.

```{r}
d_acc_ts<- d.raw_ts %>%
  select(Subject_ID, acc1, acc2, acc3, acc4, acc5, acc6, acc7, acc8, acc9, acc10, acc11, acc12, acc13, acc14, acc15, acc16, acc17, acc18, acc19, acc20)%>%
  gather(trial, acc, acc1:acc20) 

d_rt <- d.raw_ts %>%
  select(Subject_ID, RT1, RT2, RT3, RT4, RT5, RT6, RT7, RT8, RT9, RT10, RT11, RT12, RT13, RT14, RT15, RT16, RT17, RT18, RT19, RT20) %>%
  gather(trial, RT, RT1:RT20) 

d_acc_ts$trial <-str_replace(d_acc_ts$trial, "acc","")
d_rt$trial <- str_replace(d_rt$trial, "RT","")

d_ts <- d_acc_ts %>%
  left_join(d_rt) %>%
  mutate(ID = Subject_ID) %>%
  select(ID, RT, acc, trial)

d_ts$acc[d_ts$acc==999] <- NA
```

Read in trial info, demographics, and word familiarity.

```{r}
demo <- read.csv("demographics.csv") 
trial_info <- read.csv("conditions.csv", header = TRUE)
trial_info$trial <- as.character(trial_info$trial)

word_fam_key <- read.csv("word_fam_key.csv")
word_fam_key$trial <- as.character(word_fam_key$trial)

word_fam <- read.csv("word_familiarity.csv") %>%
  gather("target", "familiarity", 2:41 )

response_key <- read.csv("response_key.csv")
response_key$trial <- as.character(response_key$trial)
```

Join trial info and demographics with raw data.

```{r}
d_ts <- left_join(d_ts, trial_info) %>%
  left_join(demo) %>%
  select(-participation_date, -birthdate) %>%
  left_join(word_fam_key) %>%
  left_join(word_fam) %>%
  left_join(response_key) %>%
  filter(drop != 1)

d_ts <- d_ts %>% 
  mutate(similar = ifelse(similarity == 1, "similar",
                                       "dissimilar")) %>%
  select(-similarity)

#how many touchscreen participants?
d_ts$ID <- as.factor(as.character(d_ts$ID))
length(levels(d_ts$ID))
```


```{r}
d.raw_et <- read.csv("AllSubs_ET.csv", header = TRUE) 
d.raw_sw <- read.csv("perceptual_transitions.csv", header = TRUE)
d.raw_sw$ID <- d.raw_sw$Subject
```

Make data tidy.

```{r}
d.raw_sw <- d.raw_sw %>%
  gather(trial, trans, Trial1:Trial20) %>%
  select(-Subject) 

#how many ET participants with transitions data?
d.raw_sw$ID <- as.factor(as.character(d.raw_sw$ID))
length(levels(d.raw_sw$ID))

#how many ET participants with accuracy data?
d.raw_et$ID <- as.factor(as.character(d.raw_et$ID))
length(levels(d.raw_et$ID))
  
d.raw_sw$trial <- str_replace(d.raw_sw$trial, "Trial","")
d.raw_et$trial <- as.character(d.raw_et$trial)

d.raw_et <- d.raw_et %>%
  select(ID, trial, acc)

d.raw_sw$ID <- as.character(d.raw_sw$ID)
d.raw_et$ID <- as.character(d.raw_et$ID)
demo$ID <- as.character(demo$ID)
word_fam$ID <- as.character(word_fam$ID)

d_et <- d.raw_et %>%
  inner_join(d.raw_sw) %>%
  mutate(acc_et = acc) %>%
  left_join(demo) %>%
  left_join(trial_info)%>%
  select(-participation_date, -birthdate) %>%
  left_join(word_fam_key) %>%
  left_join(word_fam) %>%
  left_join(response_key) %>%
  filter(drop != 1) %>%
  select(-acc)

d_et <- d_et %>% 
  mutate(similar = ifelse(similarity == 1, "similar",
                                       "dissimilar")) %>%
  select(-similarity)

#how many total ET participants with both transitions and accuracy data?
d_et$ID <- as.factor(as.character(d_et$ID))
length(levels(d_et$ID))
```

Merge TS and ET data.

```{r}
d <- d_ts %>%
  full_join(d_et) %>%
  filter(drop != 1)
#how many with either TS OR ET data?
# d$ID <- as.factor(as.character(d$ID))
# length(levels(d$ID))
```

Demographics.

```{r}
demo_drop <- demo %>%
  filter(drop != 1)

table(demo_drop$income)
table(demo_drop$age_months)
table(demo_drop$race)
```


Descriptives.

```{r}
d_et_filt <- d_et %>% 
  filter(!is.na(trans),
         !is.na(acc_et),
         familiarity != 0)

#how many participants in full filtered ET file?
d_et_filt$ID <- as.factor(d_et_filt$ID)
length(levels(d_et_filt$ID))
```

Plot correct and incorrect trans distributions

```{r}
d_et_filt$acc <- as.factor(d_et_filt$acc)

ggplot(aes(x = trans, fill = acc), 
       data = d_et_filt) +
  geom_density(alpha = 0.7, adjust = 1.5) + 
  facet_grid(.~similar) 
```

```{r}
d_et_filt$acc <- as.numeric(d_et_filt$acc)

ms <- d_et_filt %>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc_et", na.rm = TRUE)

ggplot(ms, aes(x = factor(similar), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Similarity") + 
  ylab("Proportion Accurate ET")

ms <- d_et_filt %>%
  group_by(acc_et, similar)%>%
  multi_boot_standard(col = "trans", na.rm = TRUE)

ggplot(ms, aes(x = factor(acc_et), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Accuracy") + 
  ylab("Number of switches") + 
  facet_wrap(~similar)

d_et_filt <- d_et_filt %>%
  mutate(stim_pair = paste(condition, trial))

ms
```

```{r}
glm_maximal_mod_trans <- lmer(trans ~ acc_et * similar +
                           (1 | ID), 
                         data = d_et_filt)

coefs <- data.frame(coef(summary(glm_maximal_mod_trans)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs

describeBy(d_et_filt$trans, d_et_filt$similar)
describeBy(d_et_filt$trans, d_et_filt$acc_et)

# d_et_filt$acc <- as.factor(as.character(d_et_filt$acc))
# d_et_filt$trial <- as.factor(d_et_filt$trial)
# 
# d_et_filt <- d_et_filt %>%
#   select(ID, trial, similar, acc_et) %>%
#   spread(similar, acc_et)
# 
# d_et_filt$dissimilar <- as.numeric(d_et_filt$dissimilar)
# d_et_filt$similar <- as.numeric(d_et_filt$similar)
# 
# write.table(d_et_filt,paste('for_ttest.csv',sep=""), sep=",",row.names=FALSE)
```

Now the TS data.

Filter fast and slow RTs, missing data, unfamiliar trials.

```{r}
top_bound <- mean(log(d_ts$RT)) + 3*sd(log(d_ts$RT))
bottom_bound <- mean(log(d_ts$RT)) - 3*sd(log(d_ts$RT))

d_filt_rt <- d_ts %>%
  filter(log(RT) < top_bound, 
         log(RT) > bottom_bound,
         !is.na(acc),
         familiarity != 0)

d_filt_rt_log <- d_filt_rt
d_filt_rt_log$RT <- log(d_filt_rt_log$RT)

```

Plot correct and incorrect RT distributions

```{r}
d_filt_rt$acc <- as.factor(d_filt_rt$acc)

ggplot(aes(x = log(RT), fill = acc), 
       data = d_filt_rt) +
  geom_density(alpha = 0.7, adjust = 1.5) + 
  facet_grid(.~similar) 
```

```{r}
d_filt_rt$acc <- as.numeric(as.character(d_filt_rt$acc))

ms <- d_filt_rt %>%
  filter(!is.na(similar))%>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms, aes(x = factor(similar), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Difficulty") + 
  ylab("Proportion Accurate TS")

ms <- d_filt_rt %>%
  filter(!is.na(acc))%>%
  group_by(acc, similar)%>%
  multi_boot_standard(col = "RT", na.rm = TRUE)

ggplot(ms, aes(x = factor(acc), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Accuracy") + 
  ylab("Mean Reaction Time (ms)") + 
  facet_wrap(~similar, labeller = label_both)
```


```{r}
glm_maximal_mod_RT <- lmer(RT ~ acc * similar +
                           (1 | ID), 
                         data = d_filt_rt)

coefs <- data.frame(coef(summary(glm_maximal_mod_RT)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs

describeBy(d_filt_rt$RT,d_filt_rt$acc)
```


Compare accuracy across tasks.

```{r}
d_compare <- d %>%
  select(ID, trial, similar, acc, acc_et, familiarity, age_months, target) %>%
  filter(familiarity != 0) %>%
  gather(task, acc, acc:acc_et) 

levels(d_compare$task) <- list(touchscreen="acc", eyetracker="acc_et")

d_compare$acc <- as.numeric(d_compare$acc)

ms <- d_compare %>%
  group_by(similar, task)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ms

ggplot(ms, aes(x = factor(similar), y = mean)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Similarity") + 
  ylab("Proportion Accurate") + 
  facet_wrap(~task, labeller = label_both)

ms <- d_compare %>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

describeBy(d_compare$acc, d_compare$similar)

```

```{r}
d_compare$acc <- as.numeric(d_compare$acc)

glm_maximal_mod_acc <- lmer(acc ~ task * similar + age_months +
                           (1 |ID), 
                         data = d_compare)

coefs <- data.frame(coef(summary(glm_maximal_mod_acc)))
# use normal distribution to approximate p-value
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs
```


# Drift Diffusion Analysis

Workflow taken from Nordmeyer et al. (2016). The goal is to estimate parameters separately for each participant and then we aggregate across participants to get means & confidence intervals on the parameters.

The parameters of the drift drift diffusion model are: 

* $\alpha$ = boundary separation: speed-accuracy tradeoff (higher values mean higher accuracy)
* $\beta$ = initial bias
* $\delta$ = drift rate: speed of information processing (close to zero means ambiguous information)
* $\tau$ = nondecision time: motor response time

## Estimating parameters

```{r setuppars}
# get the data we care about and format for Rwiener functions
# columns need to be named "q" for RT and "resp" for response
d_ddm <- d_filt_rt %>% 
  filter(RT <= 6000, RT >= 600) %>% 
  mutate(RT_sec = RT / 1000) %>% 
  select(ID, similar, RT_sec, acc, response) %>% 
  dplyr::rename(q = RT_sec)

d_ddm$acc <- as.factor(d_ddm$acc)
levels(d_ddm$acc) <- list(lower="0", upper="1")

d_ddm <- d_ddm %>% mutate(resp = acc)
```

```{r}
sub.pars <- data.frame(Separation = numeric(),
                       Non.Decision = numeric(),
                       Bias = numeric(),
                       Drift = numeric(),
                       Similar = character(),
                       Sub.Num = character(),
                       stringsAsFactors = F)

#because RWiener is finicky:
d_ddm$resp <- as.character(d_ddm$resp)
```

```{r estpars}
conditions <- unique(as.character(d_ddm$similar))
subs <- unique(as.character(d_ddm$ID)) 
sub.pars.final <- data.frame()

for (j in 1:length(subs)) {
  sid <- as.character(subs[j]) 
  print(sid)
  dat <- as.data.frame(filter(d_ddm, ID == sid))
    # fit ddm for each participant
    # and for each condition run
  for (cond in 1:length(conditions)) {
    dat_cond <- filter(dat, similar == conditions[cond])
    condition_type <- conditions[cond]
    print(condition_type)
    opt <- optim(c(1, .1, .1, 1), wiener_deviance, 
              dat=select(dat_cond, c(q, resp)), method="Nelder-Mead")
    pars <- c(opt$par, condition_type, sid)
    sub.pars[cond,] <- pars
  }
  sub.pars.final <- rbind(sub.pars.final, sub.pars)  
} 
```

### Plot Parameters

This plot shows the mean parameter values & 95% C.I.s for each stimuli type

```{r plotpars, fig.width=8, fig.height=6}
sub.pars.final$Separation <- as.numeric(sub.pars.final$Separation)
sub.pars.final$Non.Decision <- as.numeric(sub.pars.final$Non.Decision)
sub.pars.final$Bias <- as.numeric(sub.pars.final$Bias)
sub.pars.final$Drift <- as.numeric(sub.pars.final$Drift)

sub.pars.final <- sub.pars.final %>% 
  group_by(Similar) %>%
  filter(Separation < mean(Separation) + 3 * sd(Separation), 
         Separation > mean(Separation) - 3 * sd(Separation)) %>%
  filter(Non.Decision < mean(Non.Decision) + 3 * sd(Non.Decision), 
         Non.Decision > mean(Non.Decision) - 3 * sd(Non.Decision)) %>%
  filter(Bias < mean(Bias) + 3 * sd(Bias), 
         Bias > mean(Bias) - 3 * sd(Bias)) %>%
  filter(Drift < mean(Drift) + 3 * sd(Drift), 
         Drift > mean(Drift) - 3 * sd(Drift)) %>%
  ungroup() %>%
  na.omit()

sub.pars.final <- sub.pars.final %>%  gather(Param, Value, Separation:Drift)
```

Plot distributions of parameters across conditions

```{r}
ggplot(aes(x = Value, fill = Similar), 
       data = filter(sub.pars.final, Param %in% c("Drift", "Separation"))) +
  geom_density(alpha = 0.7, adjust = 1.5) + 
  facet_grid(.~Param, scales = "free") +
  scale_fill_solarized()
```

Get means and CIs for parameter values and plot

```{r}
sub.pars.ms <- sub.pars.final %>%
  group_by(Similar, Param) %>%
  multi_boot_standard(column = "Value", empirical_function = "mean")

ggplot(aes(x = Similar, y = mean), 
       data = filter(sub.pars.ms)) +
  geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~Param, scales = "free") +
  scale_fill_solarized() + 
  ylab("Mean Param Value") +
  guides(fill = F) 
```


