---
title: "Toddler Uncertainty Signals"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of toddler uncertainty signals study.


Preliminaries.

```{r, include = FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))

library(langcog)
library(dplyr)
library(RWiener)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(knitr)
library(markdown)
library(psych)
library(magrittr)
library(ez)
library(Hmisc)

select <- dplyr::select 
filter <- dplyr::filter 
summarise <- dplyr::summarise
distinct <- dplyr::distinct
mutate <- dplyr::mutate

theme_set(theme_bw())
```

#Eyetracker task

Filter unfamiliar trials (parents reported that child did not know word), and kids who performed below chance. Two participants dropped for below-chance performance (109 and 70).

```{r}
rm(list=ls())
load("data_et.RData")

#remove unfamiliar trials.
#"trans" = gaze switches
d_et_filt <- d_et %>% 
  dplyr::filter(familiarity != 0)

#remove participants who performed at chance.
mss_et_acc <-  d_et_filt
mss_et_acc$acc <- as.numeric(as.character(mss_et_acc$acc))
mss_et_acc <- mss_et_acc %>%
  group_by(ID)%>%
  summarise(acc = mean(acc))%>%
  mutate(drop_acc = acc < .5)

drop_acc <- mss_et_acc$ID[mss_et_acc$drop_acc == TRUE]

d_et_filt <- d_et_filt %>% 
  dplyr::filter(!ID %in% drop_acc)
```

##Accuracy

Get a dataframe for looking at accuracy by similarity.
```{r}
mss_et_acc_tt <-  d_et_filt 
mss_et_acc_tt$acc <- as.numeric(as.character(mss_et_acc_tt$acc))

#get mean accuracy by similarity condition.
mss_et_acc_t <- mss_et_acc_tt %>%
  group_by(ID, similar)%>%
  summarise(acc = mean(acc))%>%
  spread(similar, acc)

mss_et_acc_r <- mss_et_acc_tt %>%
  group_by(ID)%>%
  summarise(acc = mean(acc))

accet <- describeBy(mss_et_acc_r$acc)
accet$mean
accet$sd
accet$min
accet$max
```

T-test for effect of similarity on accuracy. 

```{r}
t.test(mss_et_acc_t$similar, 
       mss_et_acc_t$dissimilar, paired = TRUE)

similar <- psych::describe(mss_et_acc_t$similar)
dissimilar <- psych::describe(mss_et_acc_t$dissimilar)

similar
dissimilar

#get effect size
cohensd_acc <- abs((similar$mean - dissimilar$mean)/((similar$sd + dissimilar$sd)/2))
cohensd_acc
```

##Switches

Set up a dataframe with switches averaged by accuracy and similiarity within participants.

```{r}
mss_et_acc <-  d_et_filt %>%
  mutate(acc = ifelse(acc == 1, "acc", "inacc")) 

#get average gaze switches for three conditions: accurate-similar, accurate-dissimilar, and inaccurate.
mss_et_inacc <-  mss_et_acc%>%
  group_by(ID, acc)%>%
  summarise(trans = mean(trans))%>%
  spread(acc, trans)%>%
  select(-acc)

mss_et_acc <-  mss_et_acc%>%
  group_by(ID, acc)%>%
  summarise(trans = mean(trans))%>%
  spread(acc, trans)

mss_et_sim <-  d_et_filt %>%
  dplyr::group_by(ID, acc, similar)%>%
  dplyr::summarise(trans = mean(trans))%>%
  dplyr::filter(acc == 1)%>%
  tidyr::spread(similar, trans)%>%
  dplyr::mutate(similar_acc = similar)%>%
  dplyr::mutate(dissimilar_acc = dissimilar)

mss_et_aov <- mss_et_inacc %>%
  left_join(mss_et_sim)%>%
  dplyr::filter(!is.na(similar_acc),
         !is.na(dissimilar_acc),
         !is.na(inacc))%>%
  gather("trial_type", "trans", inacc:dissimilar_acc) %>%
  filter(trial_type != "acc",
         trial_type != "similar",
         trial_type != "dissimilar")
```

###Repeated measures ANOVA

Repeated-measures ANOVA with trial type (similar and accurate, dissimilar and accurate, and inaccurate) as the independent variable.
```{r}
ET.aov <- with(mss_et_aov,
                   aov(trans ~ trial_type +
                       Error(ID /trial_type))) #add error term for ID for repeated measures
summary(ET.aov)

ezANOVA(
mss_et_aov
, trans
, ID
, within = trial_type
, within_full = NULL
, within_covariates = NULL
, between = NULL
, between_covariates = NULL
, observed = NULL
, diff = NULL
, reverse_diff = FALSE
, type = 2
, white.adjust = FALSE
, detailed = FALSE
, return_aov = FALSE
)
```

```{r}
#get means and CIs for plot.
mss_et_aov_p <- mss_et_aov %>%
  group_by(trial_type)%>%
  multi_boot_standard(col = "trans", na.rm = TRUE)

mss_et_aov_p$trial_type <- factor(mss_et_aov_p$trial_type, 
                            levels = c("dissimilar_acc","similar_acc","inacc"))

ggplot(mss_et_aov_p, aes(x = factor(trial_type), y = mean, fill = trial_type)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Trial Type") + 
  ylab("Mean Switch Count")  +  
  theme(panel.grid = element_blank()) + #no gridlines
  scale_fill_grey() #grayscale
```

###T-tests

```{r}
t.test(subset(mss_et_aov, trial_type=="inacc")$trans, 
       subset(mss_et_aov, trial_type=="similar_acc")$trans, paired = TRUE)

t.test(subset(mss_et_aov, trial_type=="inacc")$trans, 
       subset(mss_et_aov, trial_type=="dissimilar_acc")$trans, paired = TRUE)

t.test(subset(mss_et_aov, trial_type=="similar_acc")$trans, 
       subset(mss_et_aov, trial_type=="dissimilar_acc")$trans, paired = TRUE)

#get effect sizes
inacc_et <- psych::describe(subset(mss_et_aov, trial_type=="inacc")$trans) 
sim_acc_et <- psych::describe(subset(mss_et_aov, trial_type=="similar_acc")$trans)
dissim_acc_et <- psych::describe(subset(mss_et_aov, trial_type=="dissimilar_acc")$trans)

cohensd_inacc_sim_acc_et <- abs((inacc_et$mean - sim_acc_et$mean)/((inacc_et$sd + sim_acc_et$sd)/2))
cohensd_inacc_sim_acc_et

cohensd_inacc_dissim_acc_et <- abs((inacc_et$mean - dissim_acc_et$mean)/((inacc_et$sd + dissim_acc_et$sd)/2))
cohensd_inacc_dissim_acc_et

cohensd_sim_acc_dissim_acc_et <- abs((sim_acc_et$mean - dissim_acc_et$mean)/((sim_acc_et$sd + dissim_acc_et$sd)/2))
cohensd_sim_acc_dissim_acc_et
```

Do the number of transitions differ based on whether the correct one was fixated first? No.

```{r}
mss_et_ff <-  filter(d_et_filt, !is.na(first_fix))%>%
  group_by(ID, first_fix)%>%
  summarise(trans = mean(trans))%>%
  spread(first_fix, trans)%>%
  filter(!is.na(correct) & !is.na(incorrect))

t.test(mss_et_ff$correct, mss_et_ff$incorrect, paired = TRUE)

mss_et_d <-  filter(d_et_filt, !is.na(first_fix))%>%
  group_by(ID, first_fix)%>%
  summarise(trans = mean(trans))

describeBy(mss_et_d$trans, mss_et_d$first_fix)
```

Based on trial type?

```{r}
mss_trans_acc <-  d_et_filt %>%
  mutate(acc = ifelse(acc == 1, "acc", "inacc"))%>%
  filter(!is.na(first_fix))

#get average gaze switches for three conditions: accurate-similar, accurate-dissimilar, and inaccurate.
mss_trans_inacc <-  mss_trans_acc%>%
  filter(!is.na(first_fix))%>%
  group_by(ID, acc, first_fix)%>%
  summarise(trans = mean(trans))%>%
  spread(acc, trans)%>%
  select(-acc)%>%
  spread(first_fix, inacc)%>%
  filter(!is.na(correct), !is.na(incorrect))%>%
  gather("first_fix", "inacc", correct:incorrect)

mss_trans_sim <-  d_et_filt %>%
  group_by(ID, acc, similar, first_fix)%>%
  summarise(trans = mean(trans))%>%
  filter(acc == 1, !is.na(first_fix))%>%
  spread(similar, trans)%>%
  mutate(similar_acc = similar)%>%
  mutate(dissimilar_acc = dissimilar)%>%
  select(-similar, -dissimilar)

mss_trans_sim_acc <- mss_trans_sim %>%
  select(-dissimilar_acc)%>%
  spread(first_fix, similar_acc)%>%
  filter(!is.na(correct), !is.na(incorrect))%>%
  gather("first_fix", "similar_acc", correct:incorrect)

mss_trans_dissim_acc <- mss_trans_sim %>%
  select(-similar_acc)%>%
  spread(first_fix, dissimilar_acc)%>%
  filter(!is.na(correct), !is.na(incorrect))%>%
  gather("first_fix", "dissimilar_acc", correct:incorrect)

mss_trans_aov <- mss_trans_inacc %>%
  inner_join(mss_trans_sim_acc)%>%
  select(-acc)%>%
  inner_join(mss_trans_dissim_acc)%>%
  select(-acc)%>%
  gather("trial_type", "trans", inacc:dissimilar_acc)
```


```{r}
mss_trans_aov_p <- mss_trans_aov %>%
  group_by(first_fix, trial_type)%>%
  multi_boot_standard(col = "trans", na.rm = TRUE)

ggplot(mss_trans_aov_p, aes(x = factor(first_fix), y = mean, fill = first_fix)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("First Fixation") + 
  ylab("Mean Switch Count")  +  
  facet_grid(~trial_type) +
  theme(panel.grid = element_blank()) + #no gridlines
  scale_fill_grey() #grayscale

library(car)
Anova(lm(trans ~ first_fix * trial_type, data=mss_trans_aov), type=3)
```

#Touchscreen task

filter fast and slow RTs, missing data, unfamiliar trials, and kids who performed below chance. Two participants dropped for chance performance (70 and 89). 

```{r}
load("data_ts.RData")

#filter fast and slow RTs, missing data, and unfamiliar trials.
top_bound <- mean(log(d_ts$RT)) + 3*sd(log(d_ts$RT))
bottom_bound <- mean(log(d_ts$RT)) - 3*sd(log(d_ts$RT))

d_filt_rt <- d_ts %>%
  dplyr::filter(log(RT) < top_bound, 
         log(RT) > bottom_bound,
         familiarity != 0)

#remove participants who performed below chance.
mss_ts_acc <-  d_filt_rt
mss_ts_acc$acc <- as.numeric(as.character(mss_ts_acc$acc))
mss_ts_acc <- mss_ts_acc %>%
  group_by(ID)%>%
  summarise(acc = mean(acc))%>%
  mutate(drop_acc = acc < .5)

drop_acc_ts <- mss_ts_acc$ID[mss_ts_acc$drop_acc == TRUE]

d_filt_rt <- d_filt_rt %>% 
  dplyr::filter(!ID %in% drop_acc_ts)
```

##Accuracy

Get a dataframe for looking at accuracy by similarity.
```{r}
mss_ts_acc_tt <-  d_filt_rt%>%
  group_by(ID, similar)

mss_ts_acc_tt$acc <- as.numeric(as.character(mss_ts_acc_tt$acc))

mss_ts_acc_t <- mss_ts_acc_tt %>%
  summarise(acc = mean(acc))%>%
  spread(similar, acc)

mss_ts_acc_r <- mss_ts_acc_tt %>%
  group_by(ID)%>%
  summarise(acc = mean(acc))

accts <- describeBy(mss_ts_acc_r$acc)
accts$mean
accts$sd
accts$min
accts$max
```

T-test for effect of similarity on accuracy. 

```{r}
t.test(mss_ts_acc_t$similar, 
       mss_ts_acc_t$dissimilar, paired = TRUE)

similar <- psych::describe(mss_ts_acc_t$similar)
dissimilar <- psych::describe(mss_ts_acc_t$dissimilar)
similar
dissimilar

#get effect size.
cohensd_acc <- abs((similar$mean - dissimilar$mean)/((similar$sd + dissimilar$sd)/2))
cohensd_acc
```

##RTs

Set up a dataframe with RTs averaged by accuracy and similiarity within participants.

```{r}
mss_ts_acc <-  d_filt_rt

mss_ts_acc <- mss_ts_acc %>% 
  mutate(acc = ifelse(acc == 1, "acc", "inacc")) 

#get average RTs for three conditions: accurate-similar, accurate-dissimilar, and inaccurate.
mss_ts_inacc <-  mss_ts_acc%>%
  group_by(ID, acc)%>%
  summarise(RT = mean(RT))%>%
  spread(acc, RT)%>%
  select(-acc)

mss_ts_acc <-  mss_ts_acc%>%
  group_by(ID, acc)%>%
  summarise(RT = mean(RT))%>%
  spread(acc, RT)

mss_ts_sim <-  d_filt_rt %>%
  dplyr::group_by(ID, acc, similar)%>%
  dplyr::summarise(RT = mean(RT))%>%
  dplyr::filter(acc == 1)%>%
  tidyr::spread(similar, RT)%>%
  dplyr::mutate(similar_acc = similar)%>%
  dplyr::mutate(dissimilar_acc = dissimilar)

mss_ts_aov <- mss_ts_inacc %>%
  left_join(mss_ts_sim)%>%
  dplyr::filter(!is.na(similar_acc),
         !is.na(dissimilar_acc),
         !is.na(inacc))%>%
  gather("trial_type", "RT", inacc:dissimilar_acc) %>%
  filter(trial_type != "acc",
         trial_type != "similar",
         trial_type != "dissimilar")
```

###Repeated-measures ANOVA

Repeated-measures ANOVA with trial type (similar and accurate, dissimilar and accurate, and inaccurate) as the independent variable.

```{r}
TS.aov <- with(mss_ts_aov,
                   aov(RT ~ trial_type +
                       Error(ID /trial_type))) #add error term for ID for repeated measures
summary(TS.aov)

ezANOVA(
mss_ts_aov
, RT
, ID
, within = trial_type
, within_full = NULL
, within_covariates = NULL
, between = NULL
, between_covariates = NULL
, observed = NULL
, diff = NULL
, reverse_diff = FALSE
, type = 2
, white.adjust = FALSE
, detailed = FALSE
, return_aov = FALSE
)
```

```{r, echo=FALSE}
mss_ts_aov_p <- mss_ts_aov %>%
  group_by(trial_type)%>%
  multi_boot_standard(col = "RT", na.rm = TRUE)

mss_ts_aov_p$trial_type <- factor(mss_ts_aov_p$trial_type, 
                            levels = c("dissimilar_acc","similar_acc","inacc"))

ggplot(mss_ts_aov_p, aes(x = factor(trial_type), y = mean, fill = trial_type)) + geom_bar(stat = "identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Trial Type") + 
  ylab("Mean Reaction Time (ms)")  +  
  theme(panel.grid = element_blank()) + #no gridlines
  scale_fill_grey() #grayscale
```

###T-tests

```{r}
t.test(subset(mss_ts_aov, trial_type=="inacc")$RT, 
       subset(mss_ts_aov, trial_type=="similar_acc")$RT, paired = TRUE)

t.test(subset(mss_ts_aov, trial_type=="inacc")$RT, 
       subset(mss_ts_aov, trial_type=="dissimilar_acc")$RT, paired = TRUE)

t.test(subset(mss_ts_aov, trial_type=="similar_acc")$RT, 
       subset(mss_ts_aov, trial_type=="dissimilar_acc")$RT, paired = TRUE)

inacc_ts <- psych::describe(subset(mss_ts_aov, trial_type=="inacc")$RT) 
sim_acc_ts <- psych::describe(subset(mss_ts_aov, trial_type=="similar_acc")$RT)
dissim_acc_ts <- psych::describe(subset(mss_ts_aov, trial_type=="dissimilar_acc")$RT)

#get effect sizes.
cohensd_inacc_sim_acc_ts <- abs((inacc_ts$mean - sim_acc_ts$mean)/((inacc_ts$sd + sim_acc_ts$sd)/2))
cohensd_inacc_sim_acc_ts

cohensd_inacc_dissim_acc_ts <- abs((inacc_ts$mean - dissim_acc_ts$mean)/((inacc_ts$sd + dissim_acc_ts$sd)/2))
cohensd_inacc_dissim_acc_ts

cohensd_sim_acc_dissim_acc_ts <- abs((sim_acc_ts$mean - dissim_acc_ts$mean)/((sim_acc_ts$sd + dissim_acc_ts$sd)/2))
cohensd_sim_acc_dissim_acc_ts
```
  
#Accuracy across ET and TS tasks for plot

```{r, echo = FALSE}
ms_et <- mss_et_acc_t %>%
  gather("similar", "acc", similar:dissimilar)%>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)%>%
  mutate(task = "ET")

ms_ts <- mss_ts_acc_t %>%
  gather("similar", "acc", similar:dissimilar)%>%
  group_by(similar)%>%
  multi_boot_standard(col = "acc", na.rm = TRUE)%>%
  mutate(task = "TS")

ms_acc <- full_join(ms_et, ms_ts)

ggplot(ms_acc, aes(x = factor(similar), y = mean, fill = similar)) + geom_bar(stat = "identity") + 
  facet_grid(~ task) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9)) +
  xlab("Similarity") + 
  ylab("Proportion Accurate") + ggtitle("Accuracy") +  
  theme(panel.grid = element_blank()) + #no gridlines
  scale_fill_grey() #grayscale
```

#Correlation of trial-level accuracy across tasks.

```{r}
#get matrix with trial-level accuracy for both tasks
accmat <- mss_et_acc_tt %>%
  select(ID, acc, trial)%>%
  mutate(acc_et = acc)%>%
  select(ID, trial, acc_et)%>%
  left_join(mss_ts_acc_tt)%>%
  mutate(acc_ts = acc)%>%
  select(ID, trial, acc_et, acc_ts)

cor <- rcorr(accmat$acc_et, accmat$acc_ts)
cor
```


#Correlations with age

Are the differences between condition means correlated with age in months?
```{r}
#Get age in months from raw data.
age_et <- d_et%>%
  select(ID, age_months)

age_ts <- d_ts%>%
  select(ID, age_months)

#Get dataframes with difference scores for conditions.
et_diff <- spread(mss_et_aov, trial_type, trans)%>%
  mutate(dacc_inacc = dissimilar_acc - inacc,
         sacc_inacc = similar_acc - inacc,
         dacc_sacc = dissimilar_acc - similar_acc)%>%
  left_join(age_et)

ts_diff <- spread(mss_ts_aov, trial_type, RT)%>%
  mutate(dacc_inacc = dissimilar_acc - inacc,
         sacc_inacc = similar_acc - inacc,
         dacc_sacc = dissimilar_acc - similar_acc)%>%
  left_join(age_ts)

#Get correlations of age in months with difference scores.
rcorr(et_diff$age_months, et_diff$dacc_inacc)
rcorr(et_diff$age_months, et_diff$sacc_inacc)
rcorr(et_diff$age_months, et_diff$dacc_sacc)

rcorr(ts_diff$age_months, ts_diff$dacc_inacc)
rcorr(ts_diff$age_months, ts_diff$sacc_inacc)
rcorr(ts_diff$age_months, ts_diff$dacc_sacc)
```

