---
title: "Toddler Uncertainty Signals"
author: "Emily"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
---

<style type="text/css">
body, td {
   font-size: 14px;
}
code {
  font-size: 11px;
}
pre {
  font-size: 11px;
}
</style>

Data analysis of toddler uncertainty signals study.

# Data preprocessing

Preliminaries.

```{r, include = FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache=TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))

library(langcog)
library(dplyr)
library(RWiener)
library(ggplot2)
library(rjson)
library(stringr)
library(tidyr)
library(lme4)
library(knitr)
library(markdown)
library(psych)
library(magrittr)
library(ez)
library(Hmisc)

select <- dplyr::select 
filter <- dplyr::filter 
summarise <- dplyr::summarise
distinct <- dplyr::distinct
mutate <- dplyr::mutate
gather <- tidyr::gather

theme_set(theme_bw())
```

Read in trial info, demographics, and word familiarity.

```{r}
demo <- read.csv("demographics.csv") 
trial_info <- read.csv("conditions.csv", header = TRUE)
trial_info$trial <- as.character(trial_info$trial)

word_fam_key <- read.csv("word_fam_key.csv")
word_fam_key$trial <- as.character(word_fam_key$trial)

word_fam <- read.csv("word_familiarity.csv") %>%
  gather("target", "familiarity", 2:41)

response_key <- read.csv("response_key.csv")
response_key$trial <- as.character(response_key$trial)
```

Read in raw TS data file and make tidy.

```{r}
#read in raw data.
d.raw_ts <- read.table("AllSubs_TS.txt", header = TRUE) 

#make accuracy data tidy.
d_acc_ts<- d.raw_ts %>%
  select(Subject_ID, acc1, acc2, acc3, acc4, acc5, acc6, acc7, acc8, acc9, acc10, acc11, acc12, acc13, acc14, acc15, acc16, acc17, acc18, acc19, acc20)%>%
  gather(trial, acc, acc1:acc20) 

#make rt data tidy.
d_rt <- d.raw_ts %>%
  select(Subject_ID, RT1, RT2, RT3, RT4, RT5, RT6, RT7, RT8, RT9, RT10, RT11, RT12, RT13, RT14, RT15, RT16, RT17, RT18, RT19, RT20) %>%
  gather(trial, RT, RT1:RT20) 

#join accuracy and rt data into one file.
d_acc_ts$trial <-str_replace(d_acc_ts$trial, "acc","")
d_rt$trial <- str_replace(d_rt$trial, "RT","")

d_ts <- d_acc_ts %>%
  left_join(d_rt) %>%
  mutate(ID = Subject_ID) %>%
  select(ID, RT, acc, trial)

#recode missing values to NA
d_ts$acc[d_ts$acc==999] <- NA
```

Join trial info and demographics with TS data.

```{r}
#join trial info and demo with TS data; remove missing trials and dropped participants
d_ts <- left_join(d_ts, trial_info) %>%
  left_join(demo) %>%
  left_join(word_fam_key) %>%
  left_join(word_fam) %>%
  left_join(response_key) %>%
  dplyr::filter(drop != 1, 
                !is.na(RT),
                !is.na(acc)) 

#recode similarity from 1s and 0s to string.
d_ts <- d_ts %>% 
  mutate(similar = ifelse(similarity == 1, "similar",
                                       "dissimilar")) %>%
  select(-similarity)
d_ts$ID <- as.factor(as.character(d_ts$ID))

d_ts <- d_ts %>%
  select(ID, RT, acc, trial, age_months, condition, drop, familiarity, response, similar)

#save to R data file.
save(d_ts, file = "data_ts.RData")
```

Read in ET data and make tidy.

```{r}
#read in raw data.
d.raw_et <- read.csv("AllSubs_ET.csv", header = TRUE) #acc data
load("et_trans.RData") #trans data

#make tidy.
d.raw_sw <- transitions %>%
  mutate(ID = as.factor(SID), trans = transitions)%>%
  select(-SID, - transitions) 

#all joining variables are character factors.
d.raw_sw$ID <- as.factor(as.character(d.raw_sw$ID))
d.raw_et$ID <- as.factor(as.character(d.raw_et$ID))
d.raw_sw$trial <- str_replace(d.raw_sw$trial, "Trial","")
d.raw_et$trial <- as.character(d.raw_et$trial)
d.raw_sw$ID <- as.character(d.raw_sw$ID)
d.raw_et$ID <- as.character(d.raw_et$ID)
demo$ID <- as.character(demo$ID)
word_fam$ID <- as.character(word_fam$ID)
```

Join ET switches and accuracy data and drop excluded participants (including pilots).

```{r}
d.raw_et <- d.raw_et %>%
  select(ID, trial, acc)

d_et <- d.raw_et %>%
  inner_join(d.raw_sw) %>%
  left_join(demo) %>%
  left_join(trial_info)%>%
  select(-participation_date, -birthdate) %>%
  left_join(word_fam_key) %>%
  left_join(word_fam) %>%
  left_join(response_key) %>%
  dplyr::filter(drop != 1, 
                !is.na(trans),
                !is.na(acc))

#recode similarity from 1s and 0s to string.
d_et <- d_et %>% 
  mutate(similar = ifelse(similarity == 1, "similar",
                                       "dissimilar")) %>%
  select(-similarity)
d_et$ID <- as.factor(as.character(d_et$ID))

d_et <-d_et %>%
  select(ID, trans, first_fix, fixations, acc, trial, age_months, condition, drop, familiarity, response, similar)

#save to R data file.
save(d_et, file = "data_et.RData")
```
